Rates of true polar wander in convecting planets

### 2015-04-02 tpw_rate.tex
Work

%\documentclass[extra,onecolumn]{gji}
\documentclass[extra,mreferee]{gji}
\usepackage{timet}
\usepackage{url}
\usepackage{amsmath}
\usepackage{graphicx}

@@

@@

which is simply a statement that a quasistatic body will rotate around the principle axis of its total moment of inertia.
Splitting the volume into $V_H$ and $\Delta V$ and substituting \ref{eos} we find

@@

The first term of this equation is zero due to the hydrostatic equation.  
The fourth term is negligible due to being second order in the smallness parameters $\Delta V/V_H$ and $\alpha \Delta T$.

>>>>

%\documentclass[extra,onecolumn]{gji}
\documentclass[extra,mreferee]{gji}
\usepackage{timet}
\usepackage{url}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{color, soul}

@@

\hl{This text is still causing me difficulty. Nondimensionalizing the hydrostatic equation does indeed result in an $\alpha T$ dependence.  }

@@

which is simply a statement that a quasistatic body will rotate around the principle axis of its total moment of inertia.

\hl{I suppose this could stop here. Another couple of lines of text will get to the quasistatic Liouville equation.  However, it does not really make a clear connection to the nondimensionalization }

Splitting the volume into $V_H$ and $\Delta V$ and substituting \ref{eos} we find

@@

The first term of this equation is zero due to the hydrostatic equation.  
The fourth term is negligible due to being second order in the smallness parameters $\Delta V/V_H$ and $\alpha \Delta T$.
Removing these, we find
\begin{equation}
\begin{aligned}
\int_{\Delta V} \rho_0 {\bf r \times \mitbf{\Omega} \times \mitbf{\Omega} \times {\bf r }} = 
-\int_{V_H} \rho_0 \alpha T {\bf r \times \mitbf{\Omega} \times \mitbf{\Omega} \times {\bf r }}
\end{aligned}
\end{equation}

This equation may be identified with \ref{disequilibrium}, where the mismatch of the convective moment of intertia with the spin axis is balanced by disequilibrium in the rotational deformation.

\hl{(I am not sure about this strategy for connecting the linear momentum equation with the angular momentum equation.  In particular, I could go much further, and divide $V$ into more pieces: $V = V_S + \Delta V_H + \Delta V_L + \Delta V_D$, where we have, repsectively, the spherical reference volume, the reference hydrostatic volume, the lag between the current figure and the hydrostatic figure, and the deflections of the surface.  This would produce a lot of terms...  The goal here is to show that this set of equations is consistent with the Liouville approach above, and that this set of nondimensional numbers is appropriate.)}
